---
title: "R Notebook"
output: html_notebook
---

Non-random allocation of tiles
```{r load-packages, warning=FALSE}
library(ggplot2)
library(dplyr)
library(lwgeom)
library(MexBrewer)
library(sf)
library(truchet)
```

ggplot()  + geom_sf(data = mosaic %>% st_buffer(dist = c(0.15)) %>% st_union(), color = "dodgerblue4", fill = "dodgerblue1", size = 1) + geom_sf(data = mosaic %>% st_buffer(dist = c(0.05)), size = 0.5)

Create data frame for the mosaic:
```{r}
xlim <- c(0, 10)
ylim <- c(0, 10)

# Create a data frame with the spots for tiles
container <- expand.grid(x = seq(xlim[1], xlim[2], 1),
                         y = seq(ylim[1], ylim[2], 1)) %>%
  mutate(tiles = case_when(x <= 2 | x >= 8 ~ "dl", 
                           x > 2 & x <8 ~ "dr"))
```

```{r}
st_truchet_ss(df = container) %>%
  ggplot() +
  geom_sf()
```

Create data frame for the mosaic:
```{r}
xlim <- c(0, 10)
ylim <- c(0, 10)

# Create a data frame with the spots for tiles
container <- expand.grid(x = seq(xlim[1], xlim[2], 1),
                         y = seq(ylim[1], ylim[2], 1)) %>%
  mutate(tiles = sample(c("dl", "dr"), n(), replace = TRUE))
```

Create mosaic using the designed container:
```{r}
mosaic <- st_truchet_ss(df = container)
```

Plot mosaic:
```{r}
ggplot() +
  geom_sf(data = mosaic,
          size = 2)
```

Plot with some embellishments:
```{r}
ggplot() +
  geom_sf(data = mosaic %>% 
            st_buffer(dist = c(0.20)) %>%
            st_union(), 
          color = "white", 
          fill = "dodgerblue1", 
          size = 0.5) + 
  geom_sf(data = mosaic %>% 
            st_buffer(dist = c(0.15),
                      singleSide = TRUE),
          aes(fill = x + y),
          color = NA) +
  scale_fill_gradientn(colors = mex.brewer("Revolucion")) +
  #scale_fill_distiller(palette = "RdYlBu")  +
  theme_void() +
  theme(legend.position = "none",
        panel.background = element_rect(color = NA,
                                        fill = "dodgerblue4"))
```

Plot with some embellishments:
```{r}
ggplot() +
  geom_sf(data = mosaic %>% 
            st_buffer(dist = c(0.20)) %>%
            st_union(), 
          color = "white", 
          fill = "dodgerblue1", 
          size = 0.5) + 
  geom_sf(data = mosaic,
          aes(color = sqrt(x^2 + y^2),
              size = sqrt(x^2 + y^2))) +
  scale_color_gradientn(colors = mex.brewer("Alacena")) +
  scale_size(range = c(0.5, 1.5)) +
  theme_void() +
  theme(legend.position = "none",
        panel.background = element_rect(color = NA,
                                        fill = "dodgerblue4"))
```

Create a polygon to contain the mosaic:
```{r}
 container <- matrix(c(0, 0,
                   0, 10,
                   10, 10,
                   10, 0,
                   0, 0),
                 ncol = 2,
                 byrow = TRUE)

  # Convert coordinates to polygons and then to simple features
  container <- data.frame(geometry = sf::st_polygon(list(container)) %>%
                       sf::st_sfc()) %>%
    sf::st_as_sf()
```

Split container
```{r}
container <- container%>%
  st_split(mosaic %>% st_union())
```

Extract geometries:
```{r}
container <- container %>% 
  st_collection_extract(c("POLYGON"))
```

Plot container:
```{r}
ggplot() +
  geom_sf(data = container %>% 
            mutate(id = sample(1:n(), 
                               n())),
          aes(fill = id),
          color = "white",
          size = 0.5) +
  geom_sf(data = container %>% 
            st_buffer(dist = c(-0.15)) %>%
            mutate(id = sample(1:n(), 
                               n())),
          aes(fill = id),
          color = "white",
          size = 0.5) +
  scale_fill_gradientn(colors = mex.brewer("Revolucion")) +
  theme_void() +
  theme(legend.position = "none")

ggsave("single-scale-polygons-revolucion.png")
```


Something interesting happens with positive buffers:
```{r}
ggplot() +
  # geom_sf(data = container %>% 
  #           mutate(id = sample(1:n(), 
  #                              n())),
  #         aes(fill = id),
  #         color = "white",
  #         size = 0.5) +
  geom_sf(data = container %>% 
            # Experiment with different buffer sizes
            st_buffer(dist = c(0.5)) %>%
            mutate(id = sample(1:n(), 
                               n())),
          aes(fill = id),
          color = "white",
          size = 1) +
  scale_fill_gradientn(colors = mex.brewer("Revolucion")) +
  theme_void() +
  theme(legend.position = "none")

ggsave("single-scale-polygons-revolucion-positive-buffers-2.png")
```

Something interesting happens with positive buffers:
```{r}
ggplot() +
  geom_sf(data = container %>% 
            # Experiment with different buffer sizes
            st_buffer(dist = c(0.5)) %>%
            st_intersection(container) %>%
            mutate(id = sample(1:n(), 
                               n())),
          aes(fill = id),
          color = "black",
          size = 1) +
  geom_sf(data = container %>% 
            # Experiment with different buffer sizes
            st_buffer(dist = c(0.3)) %>%
            st_buffer(dist = -0.2) %>%
            mutate(id = sample(1:n(), 
                               n())),
          fill = NA,
          color = "black",
          size = 1) +
  scale_fill_gradientn(colors = mex.brewer("Revolucion")) +
  theme_void() +
  theme(legend.position = "none")

ggsave("single-scale-polygons-revolucion-positive-buffers-3.png")
```

