---
title: "R Notebook"
output: html_notebook
---

Here I experiment with creating contours of Truchet tiles after seeing some really cool examples (see: https://twitter.com/_sayo_y/status/1488504770755440640).

I will use these packages:
```{r}
library(bezier)
library(lwgeom)
library(MexBrewer) 
library(sf)
library(tidyverse)
library(truchet)
```

Try function:
```{r}
st_truchet_flex(type = "Al", b = 1/2) %>%
  plot()
```

Design data frame with alternating values of b according to a checkerboard pattern. This is identical to the 2-by-2 arrangement of AC-CA called "design C" by Truchet (see p. 122 of Bosch and Colley, 2013):
```{r}
df <- data.frame(expand.grid(x = 1:10, 
                             y = 1:10))

df <- df %>% 
  # The modulus of x + y can be used to create a checkerboard pattern
  mutate(tiles = case_when((x + y) %% 2 == 0 ~ "Al",
                           (x + y) %% 2 == 1 ~ "Cl"),
         b = 1/2)
# b = ifelse((x + y) %% 2 == 1, 1/3, 2/3))
```

Create mosaic:
```{r}
mosaic <- st_truchet_fm(df = df)
```

Plot:
```{r}
mosaic %>%
  ggplot() + 
  geom_sf(aes(fill = color),
          color = "white") +
  scale_fill_distiller(direction = 1)
```

Data frame with random values of b:
```{r}
df <- data.frame(expand.grid(x = 1:10, 
                             y = 1:10))

df <- df %>% 
  # The modulus of x + y can be used to create a checkerboard pattern
  mutate(tiles = case_when((x + y) %% 2 == 0 ~ "Al",
                           (x + y) %% 2 == 1 ~ "Cl"),
         b = runif(n(), 1/3, 1/2))
```

Create mosaic:
```{r}
mosaic <- st_truchet_fm(df = df)
```

Plot:
```{r}
mosaic %>%
  st_truchet_dissolve() %>%
  ggplot() + 
  geom_sf(aes(fill = color),
          color = "white") +
  scale_fill_distiller(direction = 1)
```

"Design D" is as follows:
$$
\begin{array}\\
B & A\\
C & D
\end{array}
$$
Recreate this design:
```{r}
df <- data.frame(expand.grid(x = 1:10, 
                             y = 1:10))

df <- df %>% 
  # The modulus of x + y can be used to create the desired pattern
  mutate(tiles = case_when(x %% 2 == 1 & y %% 2 == 0 ~ "Bl",
                           x %% 2 == 0 & y %% 2 == 0 ~ "Al",
                           x %% 2 == 1 & y %% 2 == 1 ~ "Cl",
                           x %% 2 == 0 & y %% 2 == 1 ~ "Dl"),
         b = 1/2)
```

Create mosaic:
```{r}
mosaic <- st_truchet_fm(df = df)
```

Plot:
```{r}
ggplot() +
  geom_sf(data = mosaic,
          aes(fill = color),
          color = "white",
          size = 0.5) + 
  scale_fill_distiller(direction = 1)
```

"Design E" appears in the article as:
$$
\begin{array}\\
C & B\\
D & A
\end{array}
$$
Recreate this design:
```{r}
df <- data.frame(expand.grid(x = 1:10, 
                             y = 1:10))

df <- df %>% 
  # The modulus of x + y can be used to create the desired pattern
  mutate(tiles = case_when(x %% 2 == 1 & y %% 2 == 0 ~ "Al",
                           x %% 2 == 0 & y %% 2 == 0 ~ "Dl",
                           x %% 2 == 1 & y %% 2 == 1 ~ "Bl",
                           x %% 2 == 0 & y %% 2 == 1 ~ "Cl"),
         b = 1/2)
```

Create mosaic:
```{r}
mosaic <- st_truchet_fm(df = df)
```

Plot (notice the difference with figure 2 in Bosch and Colley):
```{r}
ggplot() +
  geom_sf(data = mosaic,
          aes(fill = color),
          color = "white",
          size = 0.5) + 
  scale_fill_distiller(direction = 1)
```


The  mosaic above looks different because "Design E" in Figure 2 in Bosch and Colley is actually a 4 by 4 matrix:
$$
\begin{array}\\
B & C & D & A\\
A & D & C & B\\
D & A & B & C\\
C & B & D & A\\
\end{array}
$$

Recreate this design:
```{r}
df <- data.frame(expand.grid(x = 1:12, 
                             y = 1:12))

df <- df %>% 
  mutate(tiles = case_when(y %% 4 == 1 & x %% 4 == 1 ~ "Bl",
                           y %% 4 == 1 & x %% 4 == 2 ~ "Cl",
                           y %% 4 == 1 & x %% 4 == 3 ~ "Dl",
                           y %% 4 == 1 & x %% 4 == 0 ~ "Al",
                           # Second Row
                           y %% 4 == 2 & x %% 4 == 1 ~ "Al",
                           y %% 4 == 2 & x %% 4 == 2 ~ "Dl",
                           y %% 4 == 2 & x %% 4 == 3 ~ "Cl",
                           y %% 4 == 2 & x %% 4 == 0 ~ "Bl",
                           # Third Row
                           y %% 4 == 3 & x %% 4 == 1 ~ "Dl",
                           y %% 4 == 3 & x %% 4 == 2 ~ "Al",
                           y %% 4 == 3 & x %% 4 == 3 ~ "Bl",
                           y %% 4 == 3 & x %% 4 == 0 ~ "Cl",
                           # Fourth Row
                           y %% 4 == 0 & x %% 4 == 1 ~ "Cl",
                           y %% 4 == 0 & x %% 4 == 2 ~ "Bl",
                           y %% 4 == 0 & x %% 4 == 3 ~ "Al",
                           y %% 4 == 0 & x %% 4 == 0 ~ "Dl"),
         b = 1/2)
```

Create mosaic:
```{r}
mosaic <- st_truchet_fm(df = df)
```

Plot:
```{r}
ggplot() +
  geom_sf(data = mosaic,
          aes(fill = color),
          color = "white",
          size = 0.5) + 
  scale_fill_distiller(direction = 1)
```

"Design 1" attributed to Douat by Bosch and Colley is based on a 2 by 4 matrix:
$$
\begin{array}\\
D & A & C & B\\
A & D & B & C\\
\end{array}
$$

Recreate this design:
```{r}
df <- data.frame(expand.grid(x = 1:12, 
                             y = 1:12))

df <- df %>% 
  mutate(tiles = case_when(y %% 2 == 1 & x %% 4 == 1 ~ "Dl",
                           y %% 2 == 1 & x %% 4 == 2 ~ "Al",
                           y %% 2 == 1 & x %% 4 == 3 ~ "Cl",
                           y %% 2 == 1 & x %% 4 == 0 ~ "Bl",
                           # Second Row
                           y %% 2 == 0 & x %% 4 == 1 ~ "Al",
                           y %% 2 == 0 & x %% 4 == 2 ~ "Dl",
                           y %% 2 == 0 & x %% 4 == 3 ~ "Bl",
                           y %% 2 == 0 & x %% 4 == 0 ~ "Cl"),
         b = 1/2)
```

Create mosaic:
```{r}
mosaic <- st_truchet_fm(df = df)
```

Plot:
```{r}
ggplot() +
  geom_sf(data = mosaic,
          aes(fill = color),
          color = "white",
          size = 0.5) + 
  scale_fill_distiller(direction = 1)
```

"Design 6" attributed to Douat by Bosch and Colley is based on a 4 by 4 matrix:
$$
\begin{array}\\
C & B & C & B\\
B & D & A & C\\
A & C & B & D\\
D & A & D & A\\
\end{array}
$$

Recreate this design:
```{r}
df <- data.frame(expand.grid(x = 1:12, 
                             y = 1:12))

df <- df %>% 
  mutate(tiles = case_when(y %% 4 == 1 & x %% 4 == 1 ~ "Cl",
                           y %% 4 == 1 & x %% 4 == 2 ~ "Bl",
                           y %% 4 == 1 & x %% 4 == 3 ~ "Cl",
                           y %% 4 == 1 & x %% 4 == 0 ~ "Bl",
                           # Second Row
                           y %% 4 == 2 & x %% 4 == 1 ~ "Bl",
                           y %% 4 == 2 & x %% 4 == 2 ~ "Dl",
                           y %% 4 == 2 & x %% 4 == 3 ~ "Al",
                           y %% 4 == 2 & x %% 4 == 0 ~ "Cl",
                           # Third Row
                           y %% 4 == 3 & x %% 4 == 1 ~ "Al",
                           y %% 4 == 3 & x %% 4 == 2 ~ "Cl",
                           y %% 4 == 3 & x %% 4 == 3 ~ "Bl",
                           y %% 4 == 3 & x %% 4 == 0 ~ "Dl",
                           # Fourth Row
                           y %% 4 == 0 & x %% 4 == 1 ~ "Dl",
                           y %% 4 == 0 & x %% 4 == 2 ~ "Al",
                           y %% 4 == 0 & x %% 4 == 3 ~ "Dl",
                           y %% 4 == 0 & x %% 4 == 0 ~ "Al"),
         b = 1/2)
```

Create mosaic:
```{r}
mosaic <- st_truchet_fm(df = df)
```

Plot:
```{r}
ggplot() +
  geom_sf(data = mosaic,
          aes(fill = color),
          color = "white",
          size = 0.5) + 
  scale_fill_distiller(direction = 1)
```

Try with buffers:
```{r}
ggplot() +
  geom_sf(data = mosaic,
          aes(fill = color),
          color = NA,
          size = 0.5) + 
  geom_sf(data = mosaic %>%
            st_truchet_dissolve() %>%
            st_buffer(dist = c(-0.1)) %>%
            filter(color == 2),
          fill = NA,
          color = "white",
          size = 0.5) + 
  geom_sf(data = mosaic %>%
            st_truchet_dissolve() %>%
            st_buffer(dist = c(-0.2)) %>%
            filter(color == 2),
          fill = NA,
          color = "white",
          size = 0.5) + 
  scale_fill_distiller(direction = 1) + 
  theme_void() +
  theme(legend.position = "none")
```

Take a 2 by 2 mosaic and assign tiles randomly:
```{r}
# Set seed
seed <- 84467
set.seed(seed)

# Coordinates for tiles
df <- data.frame(expand.grid(x = 1:10, 
                             y = 1:10))

# Randomly select tiles
tiles <- sample(c("Al", "Bl", "Cl", "Dl"), size = 4, replace = TRUE)

# Design the mosaic
df <- df %>% 
  # The modulus of x + y can be used to create the desired pattern
  mutate(tiles = case_when(x %% 2 == 1 & y %% 2 == 0 ~ tiles[1],
                           x %% 2 == 0 & y %% 2 == 0 ~ tiles[2],
                           x %% 2 == 1 & y %% 2 == 1 ~ tiles[3],
                           x %% 2 == 0 & y %% 2 == 1 ~ tiles[4]),
         b = 1/2)

# Assemble mosaic
mosaic <- st_truchet_fm(df = df)

# Plot:
ggplot() +
  geom_sf(data = mosaic %>%
            st_truchet_dissolve(),
          aes(fill = color),
          color = NA,
          size = 0.5) + 
  geom_sf(data = mosaic %>%
            st_truchet_dissolve() %>%
            st_buffer(dist = c(-0.15)) %>%
            filter(color == 2),
          fill = NA,
          color = "white",
          size = 0.5) + 
  scale_fill_distiller(direction = 1) + 
  theme_void() +
  theme(legend.position = "none")

ggsave(glue::glue("truchet_2x2_{seed}.png"))
```

Take a 4 by 4 mosaic and assign tiles randomly:
```{r}
# Set seed
seed <- 298265805
set.seed(seed)

# Coordinates for tiles
df <- data.frame(expand.grid(x = 1:10, 
                             y = 1:10))

# Randomly select tiles
tiles_1 <- sample(c("Al", "Bl", "Cl", "Dl"), size = 4, replace = TRUE)
tiles_2 <- sample(c("Al", "Bl", "Cl", "Dl"), size = 4, replace = TRUE)
tiles_3 <- sample(c("Al", "Bl", "Cl", "Dl"), size = 4, replace = TRUE)
tiles_4 <- sample(c("Al", "Bl", "Cl", "Dl"), size = 4, replace = TRUE)

df <- data.frame(expand.grid(x = 1:12, 
                             y = 1:12))

df <- df %>% 
  mutate(tiles = case_when(y %% 4 == 1 & x %% 4 == 1 ~ tiles_1[1],
                           y %% 4 == 1 & x %% 4 == 2 ~ tiles_1[2],
                           y %% 4 == 1 & x %% 4 == 3 ~ tiles_1[3],
                           y %% 4 == 1 & x %% 4 == 0 ~ tiles_1[4],
                           # Second Row
                           y %% 4 == 2 & x %% 4 == 1 ~ tiles_2[1],
                           y %% 4 == 2 & x %% 4 == 2 ~ tiles_2[2],
                           y %% 4 == 2 & x %% 4 == 3 ~ tiles_2[3],
                           y %% 4 == 2 & x %% 4 == 0 ~ tiles_2[4],
                           # Third Row
                           y %% 4 == 3 & x %% 4 == 1 ~ tiles_3[1],
                           y %% 4 == 3 & x %% 4 == 2 ~ tiles_3[2],
                           y %% 4 == 3 & x %% 4 == 3 ~ tiles_3[3],
                           y %% 4 == 3 & x %% 4 == 0 ~ tiles_3[4],
                           # Fourth Row
                           y %% 4 == 0 & x %% 4 == 1 ~ tiles_4[1],
                           y %% 4 == 0 & x %% 4 == 2 ~ tiles_4[2],
                           y %% 4 == 0 & x %% 4 == 3 ~ tiles_4[3],
                           y %% 4 == 0 & x %% 4 == 0 ~ tiles_4[4]),
         b = 1/2)

# Assemble mosaic
mosaic <- st_truchet_fm(df = df)

# Plot:
ggplot() +
  geom_sf(data = mosaic %>%
            st_truchet_dissolve(),
          aes(fill = color),
          color = NA,
          size = 0.5) + 
  geom_sf(data = mosaic %>%
            st_truchet_dissolve() %>%
            st_buffer(dist = c(-0.15)) %>%
            filter(color == 2),
          fill = NA,
          color = "white",
          size = 0.5) + 
  scale_fill_distiller(direction = 1) + 
  theme_void() +
  theme(legend.position = "none")

ggsave(glue::glue("truchet_4x4_{seed}.png"))
```

## Figurative mosaics

Load package to work with images:
```{r}
library(imager)
```

Read the image using `imager::load.image()`:
```{r}
#melville <- image_read("melville_lg.jpg")
elvis <- load.image("elvis.jpg")
```

Image info:
```{r}
elvis
```

```{r}
plot(elvis)
```

Resize image:
```{r}
elvis_rs <- imresize(elvis, scale = 1/10, interpolation = 6)
```

Convert to grayscale and to data frame:
```{r}
elvis_df <- elvis_rs %>%
  grayscale() %>% 
  as.data.frame()
```

Use this data frame to design truchet mosaic:
```{r}
df <- elvis_df %>% 
  # Reverse the y axis
  mutate(y = -(y - max(y)),
         # The modulus of x + y can be used to create a checkerboard pattern
         tiles = case_when((x + y) %% 2 == 0 ~ "Al",
                           (x + y) %% 2 == 1 ~ "Cl"),
         b = case_when((x + y) %% 2 == 0 ~ 1 - value,
                       (x + y) %% 2 == 1 ~ value))
```

Create mosaic and time process (it takes about 4 minutes to process an image of 200 by 300 pixels or so):
```{r}
# Start a timer
start_time <- Sys.time()

# Assemble mosaic
mosaic <- st_truchet_fm(df = df %>% mutate(b = b * 0.99 + 0.001))

# End timer
end_time <- Sys.time()

# Calculate time
end_time - start_time
```

Plot:
```{r}
mosaic %>%
  ggplot() + 
  geom_sf(aes(fill = color),
          color = NA) +
  scale_fill_distiller(direction = 1) + 
  theme_void() +
  theme(legend.position = "none")

ggsave("elvis-truchet.png")
```


Read another image:
```{r}
frida <- load.image("frida.jpg")
```

Image info:
```{r}
frida
```

```{r}
plot(frida)
```

Resize image:
```{r}
frida_rs <- imresize(frida, scale = 1/3, interpolation = 6)
```

Convert to grayscale and to data frame:
```{r}
frida_df <- frida_rs %>%
  grayscale() %>% 
  as.data.frame()
```

Use this data frame to design truchet mosaic:
```{r}
df <- frida_df %>% 
  # Reverse the y axis
  mutate(y = -(y - max(y)),
         # The modulus of x + y can be used to create a checkerboard pattern
         tiles = case_when((x + y) %% 2 == 0 ~ "Al",
                           (x + y) %% 2 == 1 ~ "Cl"),
         b = case_when((x + y) %% 2 == 0 ~ 1 - value,
                       (x + y) %% 2 == 1 ~ value))
```

Create mosaic:
```{r}
# Start a timer
start_time <- Sys.time()

# Assemble mosaic
mosaic <- st_truchet_fm(df = df %>% mutate(b = b * 0.80 + 0.001))

# End timer
end_time <- Sys.time()

# Calculate time
end_time - start_time
```

Plot:
```{r}
mosaic %>%
  ggplot() + 
  geom_sf(aes(fill = color),
          color = NA) +
  scale_fill_gradientn(colors = mex.brewer("Frida")) + 
  theme_void() +
  theme(legend.position = "none")

ggsave("frida-truchet.png")
```



<!--

Data frame with random selection of tiles and random values of b:
```{r}
df <- data.frame(expand.grid(x = 1:10, 
y = 1:10))

df <- df %>% 
# The modulus of x + y can be used to create a checkerboard pattern
mutate(tiles = sample(c("Al", "Bl"), n(), replace = TRUE),
b = runif(n(), 0, 1))
```

Create mosaic and join coordinates. The coordinates can be used to modify the color settings according to a checkerboard pattern:
```{r}
mosaic <- st_truchet_fm(df = df)
```

Plot:
```{r}
mosaic %>%
st_truchet_dissolve() %>%
ggplot() + 
geom_sf(aes(fill = color),
color = "white")
```

Plot after adding some buffering:
```{r}
ggplot() + 
geom_sf(data = mosaic %>%
st_truchet_dissolve() %>% 
mutate(id = sample(1:n(), 
n())),
aes(fill = id),
color = "black",
size = 0.5) +
geom_sf(data = mosaic %>%
st_truchet_dissolve() %>%
st_buffer(dist = c(-0.1, -0.2)) %>% 
mutate(id = sample(1:n(), 
n())),
aes(fill = id),
color = "black",
size = 0.5) +
scale_fill_gradientn(colors = mex.brewer("Revolucion")) +
theme_void() +
theme(legend.position = "none")
```

More buffers:
```{r}
ggplot() + 
geom_sf(data = mosaic %>%
st_truchet_dissolve() %>% 
mutate(id = sample(1:n(), 
n())),
aes(fill = id),
color = "black",
size = 0.5) +
geom_sf(data = mosaic %>%
st_truchet_dissolve() %>%
st_buffer(dist = c(-0.1)) %>% 
mutate(id = sample(1:n(), 
n())),
aes(fill = id),
color = "black",
size = 0.5) +
geom_sf(data = mosaic %>%
st_truchet_dissolve() %>%
st_buffer(dist = c(-0.2)) %>% 
mutate(id = sample(1:n(), 
n())),
aes(fill = id),
color = "black",
size = 0.5) +
scale_fill_gradientn(colors = mex.brewer("Revolucion")) +
theme_void() +
theme(legend.position = "none")

ggsave("flex-tiles-random-revolucion-buffers.png")
```

