---
title: "Figurative Portrait with Truchet Tiles"
output: html_notebook
---

Load packages:
```{r load-packages, warning=FALSE}
library(ggplot2)
library(imager)
library(dplyr)
library(lwgeom)
library(MexBrewer)
library(purrr)
library(sf)
library(truchet)
```


## Create a figurative mosaic

Read the image using `imager::load.image()`:
```{r}
jn <- load.image("annya-color-Photoroom.jpeg")
```

Image info:
```{r}
jn
```

This is the image:
```{r}
plot(jn)
```

Resize image:
```{r}
jn_rs <- imresize(jn, scale = 1/3, interpolation = 6)
jn_rs
```

Pad:
```{r}
jn_rs <- jn_rs |>
  pad(-40, "y", pos = -1, val = "white") |>
  #pad(22, "y", pos = 1) |>
  pad(10, "x", pos = -1, val = "white") |>
  pad(18, "x", pos = 1, val = "white") |>
  plot()
```

Convert to data frame:
```{r}
df <- jn_rs %>% 
  grayscale() %>% 
  as.data.frame()
```

```{r}
df_color <- jn_rs %>%
  as.data.frame(wide="c") %>% 
  # Reverse the y axis
  mutate(y = -(y - max(y)),
         hex_color = rgb(c.1,
                         c.2,
                         c.3))
```

```{r}
# Set seed
# seed <- 1085
# set.seed(seed)
# 
# # Randomly select tiles
# tiles <- sample(c("Al", "Bl", "Cl", "Dl"), size = 4, replace = TRUE)
# 
# value <- 3/4
# # Design the mosaic
# df <- df %>% 
#   # Reverse the y axis
#   mutate(y = -(y - max(y)),
#          tiles = case_when(x %% 2 == 1 & y %% 2 == 0 ~ tiles[1],
#                            x %% 2 == 0 & y %% 2 == 0 ~ tiles[2],
#                            x %% 2 == 1 & y %% 2 == 1 ~ tiles[3],
#                            x %% 2 == 0 & y %% 2 == 1 ~ tiles[4]),
#          # Important! Notice the adjustment to the values to ensure that the area correctly reflects the underlying darkness value
#          b = case_when(tiles == "Al" ~ 1- value, 
#                        tiles == "Bl" ~ 1- value, 
#                        tiles == "Cl" ~ value, 
#                        tiles == "Dl" ~ value))

df <- df %>% 
  # Reverse the y axis
  mutate(y = -(y - max(y)),
         # The modulus of x + y can be used to create a checkerboard pattern
         tiles = case_when((x + y) %% 2 == 0 ~ "Al",
                           (x + y) %% 2 == 1 ~ "Cl"),
         b = case_when((x + y) %% 2 == 0 ~ 1 - value,
                       (x + y) %% 2 == 1 ~ value))

# Assemble mosaic
mosaic <- st_truchet_fm(df = df %>% mutate(b = b * 0.99 + 0.001))

# Plot
mosaic %>%
  ggplot() + 
  geom_sf(aes(fill = color),
          color = NA) +
  scale_fill_distiller(direction = 1) + 
  coord_sf(expand = FALSE) +
  theme_void() +
  theme(legend.position = "none")

ggsave(filename = "annya-duotone.pdf",
       width = 8.5,
       height = 11,
       units = "in")
```

Convert color data frame to simple features to use {sf} functionality:
```{r}
df_color_sf <- df_color %>%
  st_as_sf(coords = c("x", "y"))
```

Borrow color from nearest geometry
```{r}
hex_color <- df_color_sf[mosaic %>% 
                               st_nearest_feature(df_color_sf),] %>%
  pull(hex_color)
```

We can now add the hexadecimal colors to the data frame with the mosaic:
```{r}
mosaic$hex_color <- hex_color
```

To plot the mosaic we use the duotone colors to filter part of the tiles. For example, here we filter duotone color 2 and use the hexadecimal colors to fill the polygons:
```{r}
mosaic %>%
  filter(color == 2) %>%
  ggplot() + 
  geom_sf(aes(fill = hex_color),
          color = NA) +
  scale_fill_identity() +
  coord_sf(expand = FALSE) +
  theme_void() +
  #theme(legend.position = "none") +
  theme(panel.background = element_rect(fill = "gray95"),
        legend.position = "none")

ggsave(filename = "annya-color.pdf",
       width = 8.5,
       height = 11,
       units = "in")
```


