---
title: "Figurative Portrait with Truchet Tiles"
output: html_notebook
---

Load packages:
```{r load-packages, warning=FALSE}
library(ggplot2) # Create Elegant Data Visualisations Using the Grammar of Graphics
library(imager) # Image Processing Library Based on 'CImg'
library(dplyr) # A Grammar of Data Manipulation
library(lwgeom) # Bindings to Selected 'liblwgeom' Functions for Simple Features
library(MexBrewer) # Color Palettes Inspired by Works of Mexican Painters and Muralists
library(purrr) # Functional Programming Tools
library(sf) # Simple Features for R
library(truchet) # Package for creating Truchet tiles and random mosaics
library(showtext) # Using Fonts More Easily in R Graphs
library(sysfonts) # Loading Fonts into R
```


## Create a figurative mosaic

Read the image using `imager::load.image()`:
```{r}
jn <- load.image("nico-01.jpeg")
```

Image info:
```{r}
jn
```

This is the image:
```{r}
plot(jn)
```

Resize image:
```{r}
jn_rs <- imresize(jn, scale = 1/10, interpolation = 6)
jn_rs
```

Pad:
```{r}
jn_rs <- pad(jn_rs, 25, "y", pos = -1) |>
  # pad(22, "y", pos = 1) |>
  # pad(90, "x", pos = -1) |>
  # pad(28, "x", pos = 1) |>
  plot()
```

Convert to data frame:
```{r}
df <- jn_rs %>% 
  grayscale() %>% 
  as.data.frame()
```

```{r use-photo-to-design-mosaic}
df <- df %>% 
  # Reverse the y axis
  mutate(y = -(y - max(y)),
         # The modulus of x + y can be used to create a checkerboard pattern
         tiles = case_when((x + y) %% 2 == 0 ~ "Al",
                           (x + y) %% 2 == 1 ~ "Cl"),
         b = case_when((x + y) %% 2 == 0 ~ 1 - value,
                       (x + y) %% 2 == 1 ~ value))
```

Add font for text:
```{r}
font_add_google("Archivo Black", family = "special")
```

Function `st_truchet_fm()` is used to create a mosaic of flexible tiles. Column `b` is scaled to avoid completely white or completely black tiles:
```{r assemble-mosaic}
# Start a timer
start_time <- Sys.time()

# Assemble mosaic
mosaic <- st_truchet_fm(df = df %>% 
                          mutate(b = b * 0.9999 + 0.00001))

# End timer
end_time <- Sys.time()

# Calculate time
end_time - start_time
```

Since the mosaic is a simple features data frame it can be plotted using `geom_sf()` in {ggplot2}:
```{r plot-mosaic}
mosaic %>% 
  mutate(color = factor(color)) |>
  ggplot() + 
  geom_sf(aes(fill = color),
          color = NA) +
  scale_fill_manual(values = c("1" = "white", "2" = "black")) + 
  coord_sf(expand = FALSE) +
  geom_rect(aes(xmin = 17, xmax = 21.5, ymin = 97.5, ymax = 102.5),
    fill = "white",
    inherit.aes = FALSE) +
  geom_rect(aes(xmin = 27, xmax = 31, ymin = 96.5, ymax = 103),
    fill = "white",
    inherit.aes = FALSE) +
  geom_rect(aes(xmin = 34, xmax = 38, ymin = 96, ymax = 102),
    fill = "white",
    inherit.aes = FALSE) +
  geom_rect(aes(xmin = 34, xmax = 35, ymin = 100, ymax = 102),
    fill = "black",
    inherit.aes = FALSE) +
  geom_rect(aes(xmin = 37, xmax = 38, ymin = 100, ymax = 102),
    fill = "black",
    inherit.aes = FALSE) +
  geom_rect(aes(xmin = 44, xmax = 48, ymin = 97.5, ymax = 102.5),
    fill = "white",
    inherit.aes = FALSE) +
  geom_text(aes(x, y), 
    data = data.frame(x = 32, y = 110), 
    label = "SCHRÖDINGER'S CAT IS",
    family = "special",
    color = "white",
    size = 4,
    fontface = "bold") +
  geom_text(aes(x, y), 
    data = data.frame(x = 28, y = 100), 
    label = "E",
    family = "special",
    color = "black",
    size = 16,
    fontface = "bold") +
  geom_text(aes(x, y), 
    data = data.frame(x = 36, y = 100), 
    label = "A",
    family = "special",
    color = "black",
    size = 16,
    fontface = "bold") +
  geom_text(aes(x, y), 
    data = data.frame(x = 25, y = 100), 
    label = "L",
    family = "special",
    color = "white",
    size = 16,
    fontface = "bold") +
  geom_text(aes(x, y), 
    data = data.frame(x = 19.5, y = 100), 
    label = "D",
    family = "special",
    color = "black",
    size = 16,
    fontface = "bold") +
   geom_text(aes(x, y), 
    data = data.frame(x = 46, y = 100), 
    label = "D",
    family = "special",
    color = "black",
    size = 16,
    fontface = "bold") +
  geom_text(aes(x, y), 
    data = data.frame(x = 14, y = 100), 
    label = "A",
    family = "special",
    color = "white",
    size = 16,
    fontface = "bold") +
  # geom_text(aes(x, y), 
  #   data = data.frame(x = 31.5, y = 100), 
  #   label = "I",
  #   family = "special",
  #   color = "white",
  #   size = 16,
  #   fontface = "bold") +
  geom_rect(aes(xmin = 30, xmax = 32.5, ymin = 96, ymax = 104),
    fill = "white",
    inherit.aes = FALSE) +
  geom_text(aes(x, y), 
    data = data.frame(x = 41, y = 100), 
    label = "V",
    family = "special",
    color = "white",
    size = 16,
    fontface = "bold") +
  geom_text(aes(x, y), 
    data = data.frame(x = 51, y = 100), 
    label = "E",
    family = "special",
    color = "white",
    size = 16,
    fontface = "bold") +
  theme_void() +
  theme(legend.position = "none",
        plot.margin=unit(c(0.125, 0.125, 0.125, 0.125), 'in'))

ggsave(filename = "schrodinger-cat.jpeg",
       width = 8,
       height = 10,
       units = "in")
```

Alternative:
```{r plot-mosaic-02}
mosaic %>% 
  mutate(color = factor(color)) |>
  ggplot() + 
  geom_sf(aes(fill = color),
          color = NA) +
  scale_fill_manual(values = c("1" = "white", "2" = "black")) + 
  coord_sf(expand = FALSE) +
  geom_rect(aes(xmin = 98, xmax = 103, ymin = 15.88, ymax = 24.12),
    fill = "black",
    inherit.aes = FALSE) +
  geom_rect(aes(xmin = 107, xmax = 111, ymin = 16.5, ymax = 23),
    fill = "black",
    inherit.aes = FALSE) +
  geom_rect(aes(xmin = 113.5, xmax = 118,5, ymin = 16, ymax = 23),
    fill = "black",
    inherit.aes = FALSE) +
  geom_rect(aes(xmin = 112, xmax = 115, ymin = 20, ymax = 24.12),
    fill = "white",
    inherit.aes = FALSE) +
  geom_rect(aes(xmin = 117, xmax = 118, ymin = 20, ymax = 22),
    fill = "white",
    inherit.aes = FALSE) +
  geom_rect(aes(xmin = 124, xmax = 131, ymin = 15.88, ymax = 24.12),
    fill = "black",
    inherit.aes = FALSE) +
  geom_text(aes(x, y), 
    data = data.frame(x = 112.5, y = 30), 
    label = "SCHRÖDINGER'S CAT IS",
    family = "special",
    color = "black",
    size = 5.5,
    fontface = "bold") +
  geom_text(aes(x, y), 
    data = data.frame(x = 108.5, y = 20), 
    label = "E",
    family = "special",
    color = "white",
    size = 17,
    fontface = "bold") +
  geom_text(aes(x, y), 
    data = data.frame(x = 116, y = 20), 
    label = "A",
    family = "special",
    color = "white",
    size = 17,
    fontface = "bold") +
  geom_text(aes(x, y), 
    data = data.frame(x = 105, y = 20), 
    label = "L",
    family = "special",
    color = "black",
    size = 17,
    fontface = "bold") +
  geom_text(aes(x, y), 
    data = data.frame(x = 99.5, y = 20), 
    label = "D",
    family = "special",
    color = "white",
    size = 17,
    fontface = "bold") +
   geom_text(aes(x, y), 
    data = data.frame(x = 126, y = 20), 
    label = "D",
    family = "special",
    color = "white",
    size = 17,
    fontface = "bold") +
  geom_text(aes(x, y), 
    data = data.frame(x = 94, y = 20), 
    label = "A",
    family = "special",
    color = "black",
    size = 17,
    fontface = "bold") +
  # geom_text(aes(x, y), 
  #   data = data.frame(x = 31.5, y = 100), 
  #   label = "I",
  #   family = "special",
  #   color = "white",
  #   size = 17,
  #   fontface = "bold") +
  geom_rect(aes(xmin = 110.9, xmax = 113, ymin = 16, ymax = 24),
    fill = "black",
    inherit.aes = FALSE) +
  geom_text(aes(x, y), 
    data = data.frame(x = 120.5, y = 20), 
    label = "V",
    family = "special",
    color = "black",
    size = 17,
    fontface = "bold") +
  geom_text(aes(x, y), 
    data = data.frame(x = 132, y = 20), 
    label = "E",
    family = "special",
    color = "black",
    size = 17,
    fontface = "bold") +
  theme_void() +
  theme(legend.position = "none",
        plot.margin=unit(c(0.125, 0.125, 0.125, 0.125), 'in'))

ggsave(filename = "schrodinger-cat-02.jpeg",
       width = 8,
       height = 10,
       units = "in")
```

