---
title: "Figurative Portrait with Truchet Tiles"
output: html_notebook
---

Load packages:
```{r load-packages, warning=FALSE}
library(ggplot2)
library(imager)
library(dplyr)
library(lwgeom)
library(MexBrewer)
library(purrr)
library(sf)
library(truchet)
```


## Create a figurative mosaic

Read the image using `imager::load.image()`:
```{r}
jn <- load.image("zeph.jpeg")
```

Image info:
```{r}
jn
```

This is the image:
```{r}
plot(jn)
```

Resize image:
```{r}
jn_rs <- imresize(jn, scale = 1/15, interpolation = 6)
jn_rs
```

Pad:
```{r}
# jn_rs <- pad(jn_rs, 90, "y", pos = -1) |>
#   pad(22, "y", pos = 1) |>
#   pad(90, "x", pos = -1) |>
#   pad(28, "x", pos = 1) |>
#   plot()
```

Convert to data frame:
```{r}
df <- jn_rs %>% 
  grayscale() %>% 
  as.data.frame()
```

```{r use-photo-to-design-mosaic}
df <- df %>% 
  # Reverse the y axis
  mutate(y = -(y - max(y)),
         # The modulus of x + y can be used to create a checkerboard pattern
         tiles = case_when((x + y) %% 2 == 0 ~ "Al",
                           (x + y) %% 2 == 1 ~ "Cl"),
         b = case_when((x + y) %% 2 == 0 ~ 1 - value,
                       (x + y) %% 2 == 1 ~ value))
```

Function `st_truchet_fm()` is used to create a mosaic of flexible tiles. Column `b` is scaled to avoid completely white or completely black tiles:
```{r assemble-mosaic}
# Start a timer
start_time <- Sys.time()

# Assemble mosaic
mosaic <- st_truchet_fm(df = df %>% 
                          mutate(b = b * 0.9999 + 0.00001))

# End timer
end_time <- Sys.time()

# Calculate time
end_time - start_time
```

Since the mosaic is a simple features data frame it can be plotted using `geom_sf()` in {ggplot2}:
```{r plot-mosaic}
mosaic %>% 
  mutate(color = factor(color)) |>
  ggplot() + 
  geom_sf(aes(fill = color),
          color = NA) +
  scale_fill_manual(values = c("1" = "white", "2" = "black")) + 
  coord_sf(expand = FALSE) +
  theme_void() +
  theme(legend.position = "none")

ggsave(filename = "zeph.pdf",
       width = 8.5,
       height = 11,
       units = "in")
```
